---
title: "Assignment 7"
author: "Munkhnaran Gankhuyag"
date: "October 14, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(dbConnect)
library(gWidgets)
library(bitops)
library(RCurl)
library(jsonlite)
library(XML)
library(knitr)
```

I created my table in SQL and I connected through R.

```{r}
con =dbConnect(MySQL(), user ='root',  host = 'localhost',
              dbname = 'CUNY')

dbListTables(con)

books <- "select * from books;"
books1 <- dbGetQuery(con,books)

```

```{r}
kable(books1)

```

First I converted my table in HTML format and uploaded in Github.

```{r}
library(tableHTML)
tableHTML(books1)

write_tableHTML(tableHTML(books1), file = "books.html")
```

Below is how structure of the table in hmtl format.

```{r}
books_html <- "https://raw.githubusercontent.com/mikegankhuyag/607-HW/master/books.html"

books_html1 <- htmlParse(getURL(books_html))
books_html1  

```
Below is the HMTL read as a table
```{r}
books_html2 <- readHTMLTable(books_html1)
kable(books_html2)
```

XML was a little easier to understand, so I wrote the table below in the format.

```{r}
books_xml <- "https://raw.githubusercontent.com/mikegankhuyag/607-HW/master/Books_xml_final.xml"
books_xml1 <- getURL(books_xml)
books_xml2 <- xmlParse(books_xml1)
books_xml2
```

Below is the XML language read as a table.

```{r}
books_xml_table <- xmlToDataFrame(books_xml2, stringsAsFactors = FALSE)
kable(books_xml_table)
```

Below is the table written in JSN format.

```{r}
books_jsn <- getURL("https://raw.githubusercontent.com/mikegankhuyag/607-HW/master/Books.json.json")
books_jsn
books_jsn2 <- fromJSON(books_jsn)

```

Below is the JSN language read as a table.
```{r}
kable(books_jsn2)
```

Overall, I had a little trouble understanding HTML format. I used to play around with it back when Myspace was popular. I can see that JSN and XML are a lot more structured and easier to read. This was a great assignment to get a feel for the different languages.

