---
title: "Assignment 3"
author: "Munkhnaran Gankhuyag"
date: "September 17, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Question 3

```{r}
library(stringr)
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555
-6542Rev. Timothy Lovejoy555 8904Ned Flanders,
5553642Dr. Julius Hibbert636-555-3226Simpson, Homer"

name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))

name
```

name_number <- data.frame(names = name, number = phone)
name_number



```{r}
switchnames <- str_split(name, ", ")
switchnames <- sapply(switchnames, function(x) str_replace(paste(x[2], x[1]),"^NA ",""))
titles <-"^(Rev|Dr)\\."
first_last <- str_replace(switchnames, titles,"")

first_last



```

```{r}
str_detect(switchnames,titles)
first_last[str_detect(first_last,"\\b[:alnum:]\\b")]

```
#Question 4

(a) [0-9]+\\$ is used for number of digits followed by the dollar sign.

```{r}
question4a <-c("917$", "data606","data607$", "assignment3$",
"data1234$67")

str_extract(question4a,"[0-9]+\\$")
```
(b) \\b[a-z]{1,4}\\b is used to extract the first lower case word that is between 2-4 characters.

```{r}
question4b <- c('Data 607 hw', 'data 607 hw', 'Data six zero seven hw')

str_extract(question4b, "\\b[a-z]{1,4}\\b")
```

(c) .*?\\.txt$ is used to extract txt files. It takes any values followed by a .txt.
```{r}
question4c <- c('data607.txt', 'Sept2017.txt', 'data607.csv', 'data.txt')
str_extract(question4c, ".*?\\.txt$")
```

(d) \\d{2}/\\d{2}/\\d{4} is used to extract date values with 2 digit days, 2 digit months and 4 digit years.
```{r}
question4d <- c('9/17/2017', '09/17/2017.txt', '09/17/2017', '09/7/2017', '9/17/17')
str_extract(question4d, "\\d{2}/\\d{2}/\\d{4}")
```


(e) <(.+?)>.+?</\\1> is used to extract for values with matching and ending with the same characters.
```{r}
question4e <- c('<Data.607>', '<a>data607</a>', '<a>data607</ab>', 607, '<607>data607.txt</607>')
str_extract(question4e, "<(.+?)>.+?</\\1>")
```


#Question 9

The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.

```{r}

Hidden_message <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

```

```{r}
str_extract_all(Hidden_message,"[[a-z]]")
str_extract_all(Hidden_message,"[[:digit:]]")
str_extract_all(Hidden_message, "[[A-Z]]")
```







